Sr: Processing Data Streams and Avoiding Work

### 2012-05-05 paper/paper.tex
Properly set the document as two column
Start related work section

\documentclass[12pt]{article}

@@

\begin{document}
\twocolumn
\maketitle

\section{Introduction}
\label{sec:intro}
One of the fundamental problems MapReduce was created to solve was processing
the growing amount of data in the world. Now with the open source Apache Hadoop
and Pig~\cite{piglatin}, it is easy to process and query the terabytes of data an organization
may collect. With terabytes of data, however, it is scarcely necessary to examine
every entry to uncover trends, especially when one only cares about the most prominent
trends or results. This type of workflow lends itself naturally to top-k-style computations,
data sampling tasks, and other cases where perfect-fidelity results are not required.
%Google runs PageRank on the entire Internet, but if
%it only did on half of the pages it crawls, it would likely still have a usable
%index for delivering the first 5 pages of results.

@@

\section{Related Work}
\label{sec:relwork}

>>>>

\documentclass[12pt,twocolumn]{article}

@@

\begin{document}
\maketitle

\section{Introduction}
\label{sec:intro}
One of the fundamental problems MapReduce was created to solve was processing
the growing amount of data in the world. Now with the open source Apache Hadoop
and Pig~\cite{Olston:2008:PLN:1376616.1376726}, it is easy to process and query
the terabytes of data an organization
may collect. With terabytes of data, however, it is scarcely necessary to examine
every entry to uncover trends, especially when one only cares about the most prominent
trends or results. This type of workflow lends itself naturally to top-k-style computations,
data sampling tasks, and other cases where perfect-fidelity results are not required.
%Google runs PageRank on the entire Internet, but if
%it only did on half of the pages it crawls, it would likely still have a usable
%index for delivering the first 5 pages of results.

@@

\section{Related Work}
\label{sec:relwork}
% data stream management system
% continuous queries
%   sr doesn't do this, instead it operates on snapshots
%   this is how online mapreduce works
% append only data sets == Chronicle data model
%   views maintained incrementally without storing any chronicles (data items)
% sequencing of streams and sliding windows
%   sr doesn't do this
% Aurora - load shedding based on app specific QoS
% approximate answers
%   baked in to Sr
%

Sr builds of previous work in the areas of MapReduce and Data Stream Management Systems.

\subsection{MapReduce}
There is a rich research field around MapReduce. This section details work related to adapting
MapReduce to a streaming environment.

The Hadoop Online Prototype~\cite{Condie:EECS-2009-136} adds streaming to the MapReduce framework
by removing the materialize phase between mappers and reducers and between phases of a
MapReduce pipeline. Results are streamed from mappers to reducers as they become available.
At any given point, each reducer maintains an in-progress snapshot of the MapReduce job's
progress up to that point. This removes the synchronization barriers inherient in MapReduce
and allows incremental progress to be observed.

This approach is in contrast to the continuous query approach taken by many other streaming
systems.

\subsection{Data Stream Management Systems}
In their overview on data stream projects~\cite{Babcock:2002:MID:543613.543615},
a new class of data streaming applications
called \emph{Data Stream Management Systems} (\emph{DSMSes}) are discussed. Sr is a type of DSMS that
includes some properties found in other systems.

The \emph{Chronicle Data Model}~\cite{Jagadish:1995:VMI:212433.220201} describes an
append-only stream of tuples. Such
streams lend themselves to incremental reads and incremental processing. In addition to incremental
updates, the Chronicle Data Model also seeks to update results incrementally without storing the
data itself.

The Aurora system~\cite{Carney:2002:MSN:1287369.1287389} introduces the concept of
\emph{load shedding}, or compensating for
resource overload by comparing job specific quality of service metrics with target levels.
